A Topic Model of Climate Change Literature

### 2017-05-03 main.tex
Update on Overleaf.

\documentclass{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author{Max Callaghan}
\begin{document}
\maketitle
\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently at least [x] times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading. We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
}

@@

>>>>

\documentclass{article}
\usepackage[a4paper, total={7in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author{Max Callaghan}
\begin{document}
\maketitle
\textbf{
To contribute to evidence-based policies on tackling climate change, the IPCC aims to comprehensively assess the relevant scientific literature \citep{IPCC2013}. With the size of this literature currently at least [x] times larger than at the time of the IPCC's first assessment report \citep{Houghton1990ClimateAssessment}, this task has become impossible without the aid of machine-reading. We collect over 300,000 abstracts from Web of Science (WoS) and Scopus, and develop a topic model in order to give an overview of this unmanageably large corpus. We find that new topics, such as [biochar] can be identified as they emerge, an application with a high potential for increasing the relevance and comprehensiveness of further IPCC reports.
}

@@

\begin{table}
\small
\setlength\tabcolsep{0.1cm}
\begin{tabular}{cccccc}
AR1 & AR2 & AR3 & AR4 & AR5 & AR6 \\
\midrule \\
\input{tables/topAR1} & \input{tables/topAR2}  & \input{tables/topAR3}
 & \input{tables/topAR4}  & \input{tables/topAR5}  & \input{tables/topAR6}
\end{tabular}
\caption{The top 5 topics in each assessment period by percentage growth since the last assessment period}
\end{table}
